---
title: "New Covid Cases and Vaccinated Population across South Asia"
author: "SA"
date: "5/29/2021"
output: html_document
---
## Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
Does the web page feature an interactive map that appears to have been created with Leaflet?
Submission






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(leaflet)
```
# Submission

## Creating Data Frame With the Following Details
#### 1.Country 2.Latitude 3.Longitude 4.New Cases in May 5.Latest Count of Vaccinated Population in May 6.Population of Country
Source: https://github.com/CSSEGISandData/COVID-19: JHU CSSE Covid-19 Data

```{r, echo=TRUE}
md_country <- data.frame(Country = c("Afghanistan","Bangladesh",
"Bhutan","India","Indonesia","Myanmar","Pakistan","Sri Lanka"),
             lat=c(33.9391,23.685,27.5142,20.5937,0.7893, 21.9162,30.3753,7.8731),
             lon = c(67.71,90.3563, 90.4336, 78.9629,  113.9213,95.956, 69.3451,80.7718),
            New_Cases = c(8621,35853,417,8390488,129131, 597,88265,66715),
            Total_Vaccinations = c(590454,9901717,482716,201203166,25782177,2994900,
6130509,1790688),
pop = c( 38928341, 164689383,  771612,  1380004385, 273523621, 54409794, 220892331,  21413250))

head(md_country,n=30)
```

## Creating New Metric - Number of Vaccinations Given as % of Population of Country
Age and other exclusion criteria for not administering vaccines are not considered
```{r, echo=TRUE}
md_country$pop_vaccine = (md_country$Total_Vaccinations/md_country$pop)*100
md_country$sqrt_cases = sqrt(md_country$New_Cases)
head(md_country)
```

## Visualization using leaflet
### Pop-up Colours - 
They denote population % Vaccinated (>=50 : Green, >=15 and < 50 : Orange, < 15 : Red), Only Bhutan is green right now while all the other countries are red.

### Labels - 
They have details on New Cases in May and Latest Vaccination Numbers respectively

### Circles 
They denote the count of new cases, highlighting the need to vaccinate quickly in countries with larger circles


```{r, echo=TRUE}
labs <- lapply(seq(nrow(md_country)), function(i) {
  paste0( '<p>', md_country[i, "Country"], '<p></p>', 
          md_country[i, "New_Cases"], '</p><p>', 
          md_country[i, "Total_Vaccinations"],'</p><p>')
       })


getColor <- function(pop_vaccine) {
  sapply(md_country$pop_vaccine, function(pop_vaccine) {
  if(pop_vaccine >= 50) {
    "green"
  } else if(pop_vaccine >=15) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(md_country)
)

md_country %>%
  leaflet() %>%
  addTiles() %>%
  addAwesomeMarkers(~lon, ~lat,icon=icons, popup = ~as.character(Country), label = lapply(labs,htmltools::HTML))%>%
  addCircles(weight = 1, radius = (md_country$sqrt_cases)*200)



```


